\chapter{Requirements Analysis}

The system is designed to be used by any user, brand or agency who are competent social media users. To understand the needs of users and to what extent their current solutions meet their needs, interviews were conducted with InCrowd. \newline \par

InCrowd is a company based in London and Brighton who provide intuitive sports technology to help brands engage with their audiences. The interviewees who work for InCrowd work in the Marketing team. Person 1 solely uses Twitter and native Twitter tools in their day to day job role. Person 2 works in the Business to Business (B2B) marketing team and focuses on using Twitter and Linkedin to achieve this role. Both interviewees use the tools and applications of the native platform but have used other industry-standard social media management tools to automate and schedule content in previous job roles. \newline \par

Functional and Non-Functional requirements are devised from the interviews conducted with InCrowd. The outcome of the requirements analysis is combined with the knowledge of the Twitter API and the overall goals and aims of the project. 

\section{Functional Requirements}

\begin{longtable}{|>{\centering}C{1.7cm}|P{7cm}|C{3.7cm}|} \hline
    {Reference} & {Description} & {Mandatory/Desirable} \\ \hline
    F1 & The system shall provide the basic functionality of what actions can be completed by a human on Twitter which can be configured and executed by the domain specific language. This functionality includes login, post tweets, reply to tweets, retweet tweets, like tweets and follow users. & Mandatory \\ \hline 
    F2 & The system shall allow scheduling for content on Twitter through the domain specific language. & Mandatory \\ \hline 
    F3 & The system shall provide the functionality to automate favouriting and retweeting tweets based on keywords through the domain specific language. & Mandatory \\ \hline
    F4 & The system shall provide the functionality to automate responding to tweets based on keywords through the domain specific language. & Mandatory \\ \hline
    F5 & The system should provide the functionality to automate direct messaging to users based on keywords through the domain specific language. & Desirable \\ \hline
    F6 & The system should retrieve a list of relevant content from other users on the platform based on a customisable input such as keywords and hashtags. & Desirable \\ \hline
    F7 & The system should provide a list of suggested accounts to follow based on inputs such as keywords and hashtags. & Desirable \\ \hline
    F8 & The system should provide the ability to customise analytical reports within a given time frame. & Desirable \\ \hline
    F9 & The system should provide a web interface to display customisable Twitter feeds. & Desirable \\ \hline
    F10 & The system should provide a web interface to display scheduled Twitter posts and content. & Desirable \\ \hline
    F10 & The system should be deployed using cloud web-services. & Desirable \\ \hline
\end{longtable}
    
\section{Non-Functional Requirements}

\begin{longtable}{|>{\centering}C{1.7cm}|P{7cm}|C{3.7cm}|}  \hline
    {Reference} & {Description} & {Mandatory/Desirable} \\ \hline
    NF1 & The domain specific language shall run on Windows, Mac and Linux Operating Systems. & Mandatory \\ \hline
    NF2 & The domain specific language shall be programmed using Python 3 and use ANTLR4 toolkit. & Mandatory \\ \hline
    NF3 & The interpreter shall run on Windows, Mac and Linux Operating Systems. & Mandatory \\ \hline
    NF4 & The interpreter shall be programmed using Python 3 and use ANTL4 toolkit. & Mandatory \\ \hline
    NF5 & The web application shall run on all latest browsers. & Desirable \\ \hline
    NF6 & The web application shall be programmed using Python 3 and Django Web Framework. & Desirable \\ \hline
    NF7 & The web application shall use Django's user login system to provide security for the web application through user authentication. & Desirable \\ \hline
    NF8 & The web application shall be deployed using AWS. & Desirable \\ \hline
\end{longtable}