\chapter{Professional Considerations}

The nature of the project using social media automation results in a broad array of ethical and professional considerations. The aims and motivations for the project are for individuals and brands to allow more automation and freedom to manage and publish their social media content; however, the project could be used in a variety of negative ways. Examples of real-world negative ethical consequences of social media automation are spam, harassment, spreading false information, troll armies and influencing content reach and impressions. \newline \par

Mitigating the risk of the tool used for negative consequences is an intricate task to be implemented into the project. To access and interact with the Twitter API, users must have authorised consumer keys and access tokens by Twitter. The pre-approved authentication allows the project to be an extension of the Twitter API by only allowing users who are pre-authorised to access the Twitter API. If the user uses the functionality of the system to violate the Developer Agreement and Policy \cite{DeveloperPolicy}, their access to the Twitter API would be revoked, and the user would not be able to use the system. \newline \par

Another ethical consequence of social media automation is spam. Twitter enforces measures to combat spam through limitations of access to the API. The Twitter API imposes rate limits, which is a per-user basis of how often users can invoke API methods. If these limits are exceeded, a time penalty will be added to the user, and the account cannot be used until these time penalties have terminated. Since the implementation of the domain specific language does not contain any direct looping or recursion, it is not necessary to directly implement rate-limits into the standard functionality of the domain specific language. The rate limits have been imposed on the automated bot scripts to combat spam and to stay within the Twitter Developer Agreement and Policy \cite{DeveloperPolicy}. Tweepy, a Python library used for accessing the Twitter API in the project, has the functionality to restrict spam. When making posts, Tweepy requires each post to be unique. If a post is not unique, a duplicate error is raised, and the post will not be posted.

\section{BSC Code of Conduct}

Ethical standards governing the conduct of computing professionals in the UK are set out in the Code of Conduct published by BCS - The Chartered Institute for IT \cite{bcs}. The project adheres to all standards set by the code of conduct. Section 1.a, Public Interest, is an essential standard as the use of automation could disregard the well-being of others through spam, and the project adheres to this standard through built-in rate-limits. All of the source code for the project will be open-source and publicly available on GitHub to uphold Section 4, Duty to Profession. The availability of the project will be in direct accordance with section 4.f, to encourage and support fellow members in their professional development. The project will not be used in practice by other users or conduct user testing; therefore no ethical review is required for the project.